---
title: "Word Bagging final_dataset.csv"
author: "Kenneth Ren"
date: "2023-08-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning = F)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(randomForest, tree, ISLR, rpart, rattle, pROC, partykit, ggplot2, glmnet, leaps, dplyr, keras, neuralnet, imager, ranger, tidyverse, RColorBrewer, wordcloud, tm, AICcmodavg, broom, ggpubr)
```

## R Markdown


```{r}
email_data <- read.csv("data/final_dataset.csv")
#email_data %>%  mutate(across(everything(), ~gsub("[[:punct:]]", "", .x)))
#remove Â
email_data$description <- iconv(email_data$description, "latin1", "ASCII", sub=" ")
email_data$description <- gsub("<.*?>", " ", email_data$description)
email_data$requirements <- iconv(email_data$requirements, "latin1", "ASCII", sub=" ")
email_data$requirements <- gsub("<.*?>", " ", email_data$requirements)
email_data$requirements <- gsub("&amp;", "&", email_data$requirements)
email_data$benefits <- iconv(email_data$benefits, "latin1", "ASCII", sub=" ")
email_data$benefits <- gsub("<.*?>", " ", email_data$benefits)
email_data$benefits <- gsub("&amp;", "&", email_data$benefits)
table(email_data$employment_type)

#gsub("<.*?>", " ", "<p>Administrative Assistant<br><br>Essential Job Responsibilities:<br><br>Answering and routing telephone calls to appropriate people<br>Scheduling appointments<br>Maintain paper and electronic filing systems for records and messages<br>Limited courier responsibilities<br>Perform any additional duties as assigned or requested<br><br>Required Qualifications:<br><br>At least two years of experience and knowledge to perform essential job functions assigned<br>Able to work in a fast-pace environment and be able to multi-task<br>Excellent communication skills and computer knowledge (QuickBooks a plus)<br>Well organized, highly dependable, and efficient<br>Must have problem solving skills and be detailed oriented<br>Maintain respect at all times for confidential information<br><br>Starting pay $25/Hr<br>Benefits:<br><br>401K Plan with company matching<br>Medical, Dental, Vision coverage<br>Vacation Pay<br>Disability insurance<br>Long-term care insurance<br>Growth Opportunities</p>")
```

## Description Column

```{r dtm_for_description}
library(tm)
text_corpus <- VCorpus(VectorSource(email_data$description))

text_corpus <- tm_map(text_corpus, content_transformer(tolower))
text_corpus <- tm_map(text_corpus, removePunctuation)
text_corpus <- tm_map(text_corpus, removeNumbers)
text_corpus <- tm_map(text_corpus, removeWords, stopwords("english"))
text_corpus <- tm_map(text_corpus, stemDocument, lazy = TRUE)
# 
dtm_description <- DocumentTermMatrix(text_corpus)
dtm_description <- removeSparseTerms(dtm_description, 1-0.05)
class(dtm_description)
inspect(dtm_description)
dim(as.matrix(dtm_description))
```
99\% sparsity

```{r}
dfdtm_description <- as.data.frame(as.matrix(dtm_description), stringsAsFactors=False)
dfdtm_description$fraudulent = email_data$fraudulent
```

We have 450 training samples, 250 testing samples, and 200 validation samples.
```{r}
N <- nrow(dfdtm_description)
index_train <- sample(N, 450)
data_description.train <- dfdtm_description[index_train,]
index_no_train <- (which(! seq(1:N) %in% index_train))
index_test <- sample(index_no_train, 250)
data_description.test <- dfdtm_description[index_test,]
index_val <- which(! index_no_train %in% index_test)
data_description.val <- dfdtm_description[index_val,]

```

Beginning LASSO
```{r}
y <- data_description.train$fraudulent
X1 <- model.matrix(fraudulent~., data = data_description.train)[,-1]
#description_result.lasso <- cv.glmnet(X1, y, alpha = 0.99, family = "binomial")
description_result.lasso <- readRDS("RDS_Saves/DescriptionLASSOv5.RDS")
#plot(description_result.lasso)
#saveRDS(description_result.lasso, file = "RDS_Saves/DescriptionLASSOv5.RDS")
#summary(description_result.lasso)

description_coef.1se <- coef(description_result.lasso, s = "lambda.min")
description_coef.1se <- description_coef.1se[which(description_coef.1se != 0),]
lasso.words.description <- rownames(as.matrix(description_coef.1se))[-1]
#lasso.words <- coef.1se@Dimnames[[1]] [coef.1se@i][-1]
#summary(lasso.words.description)
length(description_coef.1se)
description_coef.1se
  

```

```{r word cloud description for scams}
description_good.glm <- description_coef.1se[which(description_coef.1se > 0)]
description_good.glm <- description_good.glm[-1]  # take intercept out
names(description_good.glm)[1:2]  # which words are positively associated with good ratings
#good.glm
description_good.fre <- sort(description_good.glm, decreasing = TRUE) # sort the coef's
#description_good.fre
length(description_good.fre)
# hist(as.matrix(good.fre), breaks=30, col="red") 
description_good.word <- names(description_good.fre)  # good words with a decreasing order in the coeff's


cor.special <- brewer.pal(8,"Dark2")  # set up a pretty color scheme
wordcloud(names(description_good.glm), description_good.glm,  # make a word cloud
          colors=cor.special, ordered.colors=F, scale = c(5, 0.05))
```

```{r word cloud description for reals}
description_good.glm <- description_coef.1se[which(description_coef.1se < 0)]
description_good.glm <- description_good.glm[-1]  # take intercept out
names(description_good.glm)[1:2]  # which words are positively associated with good ratings
#good.glm
description_good.fre <- sort(description_good.glm, decreasing = TRUE) # sort the coef's
description_good.fre
round(description_good.fre, 4)[1:2]
length(description_good.fre)
# hist(as.matrix(good.fre), breaks=30, col="red") 
description_good.word <- names(description_good.fre)  # good words with a decreasing order in the coeff's


cor.special <- brewer.pal(8,"Dark2")  # set up a pretty color scheme
wordcloud(names(description_good.glm), description_good.glm * -1,  # make a word cloud
          colors=cor.special, ordered.colors=F, scale = c(5, 0.05))
```

## Requirements Column

```{r dtm_for_requirements}
library(tm)



text_corpus <- VCorpus(VectorSource(email_data$requirements))

text_corpus <- tm_map(text_corpus, content_transformer(tolower))
text_corpus <- tm_map(text_corpus, removePunctuation)
text_corpus <- tm_map(text_corpus, removeNumbers)
text_corpus <- tm_map(text_corpus, removeWords, stopwords("english"))
text_corpus <- tm_map(text_corpus, stemDocument, lazy = TRUE)

# 
dtm_requirements <- DocumentTermMatrix(text_corpus)
dtm_requirements <- removeSparseTerms(dtm_requirements, 1-0.05)
class(dtm_requirements)
inspect(dtm_requirements)
dim(as.matrix(dtm_requirements))
```


```{r}
dfdtm_requirements <- as.data.frame(as.matrix(dtm_requirements), stringsAsFactors=False)
dfdtm_requirements$fraudulent = email_data$fraudulent
```

We have 450 training samples, 250 testing samples, and 200 validation samples.
```{r}
N <- nrow(dfdtm_requirements)
index_train <- sample(N, 450)
data_requirements.train <- dfdtm_requirements[index_train,]
index_no_train <- (which(! seq(1:N) %in% index_train))
index_test <- sample(index_no_train, 250)
data_requirements.test <- dfdtm_requirements[index_test,]
index_val <- which(! index_no_train %in% index_test)
data_requirements.val <- dfdtm_requirements[index_val,]

```

Beginning LASSO
```{r}
colnames(data_requirements.train)[which('a' %in% colnames(data_requirements.train))]
y <- data_requirements.train$fraudulent
seedReq1 <- .Random.seed
X1 <- model.matrix(fraudulent~., data = data_requirements.train)[,-1]
seedReq2 <- .Random.seed
#requirements_result.lasso <- cv.glmnet(X1, y, alpha = 0.99, family = "binomial")
requirements_result.lasso <- readRDS("RDS_Saves/RequirementsLASSOv5.RDS")
plot(requirements_result.lasso)
#saveRDS(requirements_result.lasso, file = "RDS_Saves/RequirementsLASSOv5.RDS")
summary(requirements_result.lasso)

requirements_coef.1se <- coef(requirements_result.lasso, s = "lambda.min")
requirements_coef.1se <- requirements_coef.1se[which(requirements_coef.1se != 0),]
lasso.words.requirements <- rownames(as.matrix(requirements_coef.1se))[-1]
#lasso.words <- coef.1se@Dimnames[[1]] [coef.1se@i][-1]
summary(lasso.words.requirements)
requirements_coef.1se

# failed <- "LLL"
# for(i in 1:300) {
#   y <- data_requirements.train$fraudulent
#   #seedReq1 <- .Random.seed
#   X1 <- model.matrix(fraudulent~., data = data_requirements.train)[,-1]
#   #seedReq2 <- .Random.seed
#   requirements_result.lasso <- cv.glmnet(X1, y, alpha = 0.99, family = "binomial")
#   #plot(requirements_result.lasso)
#   #saveRDS(requirements_result.lasso, file = "RDS_Saves/RequirementsLASSOv3.RDS")
#   #summary(requirements_result.lasso)
#   
#   requirements_coef.1se <- coef(requirements_result.lasso, s = "lambda.min")
#   requirements_coef.1se <- requirements_coef.1se[which(requirements_coef.1se != 0),]
#   
#   lasso.words.requirements <- rownames(as.matrix(requirements_coef.1se))[-1]
#   #lasso.words <- coef.1se@Dimnames[[1]] [coef.1se@i][-1]
#   #summary(lasso.words.requirements)
#   if (length(requirements_coef.1se) > 12) {
#     failed <- "win"
#     break
#     lasso_max_length <- length(requirements_coef.1se)
#     good_result.lasso <- requirements_result.lasso
#   }
#   requirements_coef.1se
#   
# }
# failed
# length(requirements_coef.1se)
# requirements_coef.1se
# #saveRDS(requirements_result.lasso, file = "RDS_Saves/RequirementsLASSOv4.RDS")
```

```{r}

```
No linear combination of any of the words in requirements are useful for predicting a regression.

```{r word cloud requirements for scams}
requirements_good.glm <- requirements_coef.1se[which(requirements_coef.1se > 0)]
requirements_good.glm <- requirements_good.glm[-1]  # take intercept out
names(requirements_good.glm)[1:2]  # which words are positively associated with good ratings
#good.glm
requirements_good.fre <- sort(requirements_good.glm, decreasing = TRUE) # sort the coef's
requirements_good.fre
round(requirements_good.fre, 4)[1:2]
length(requirements_good.fre)
# hist(as.matrix(good.fre), breaks=30, col="red") 
requirements_good.word <- names(requirements_good.fre)  # good words with a decreasing order in the coeff's


cor.special <- brewer.pal(8,"Dark2")  # set up a pretty color scheme
wordcloud(names(requirements_good.glm), requirements_good.glm,  # make a word cloud
          colors=cor.special, ordered.colors=F, scale = c(5, 0.05))
```

```{r word cloud requirements for reals}
requirements_good.glm <- requirements_coef.1se[which(requirements_coef.1se < 0)]
requirements_good.glm <- requirements_good.glm[-1]  # take intercept out
names(requirements_good.glm)[1:2]  # which words are positively associated with good ratings
#good.glm
requirements_good.fre <- sort(requirements_good.glm, decreasing = TRUE) # sort the coef's
requirements_good.fre
round(requirements_good.fre, 4)[1:2]
length(requirements_good.fre)
# hist(as.matrix(good.fre), breaks=30, col="red") 
requirements_good.word <- names(requirements_good.glm)  # good words with a decreasing order in the coeff's


cor.special <- brewer.pal(8,"Dark2")  # set up a pretty color scheme
wordcloud(names(requirements_good.glm), requirements_good.glm * -1,  # make a word cloud
          colors=cor.special, ordered.colors=F, scale = c(5, 0.04))
```

## Benefits Column
```{r dtm_for_benefits}
library(tm)



text_corpus <- VCorpus(VectorSource(email_data$benefits))

text_corpus <- tm_map(text_corpus, content_transformer(tolower))
text_corpus <- tm_map(text_corpus, removePunctuation)
text_corpus <- tm_map(text_corpus, removeNumbers)
text_corpus <- tm_map(text_corpus, removeWords, stopwords("english"))
text_corpus <- tm_map(text_corpus, stemDocument, lazy = TRUE)

# 
dtm_benefits <- DocumentTermMatrix(text_corpus)
dtm_benefits <- removeSparseTerms(dtm_benefits, 1-0.05)
class(dtm_benefits)
inspect(dtm_benefits)
dim(as.matrix(dtm_benefits))

dfdtm_benefits <- as.data.frame(as.matrix(dtm_benefits), stringsAsFactors=False)
dfdtm_benefits$fraudulent = email_data$fraudulent
```

We have 450 training samples, 250 testing samples, and 200 validation samples.
```{r}
N <- nrow(dfdtm_benefits)
index_train <- sample(N, 450)
data_benefits.train <- dfdtm_benefits[index_train,]
index_no_train <- (which(! seq(1:N) %in% index_train))
index_test <- sample(index_no_train, 250)
data_benefits.test <- dfdtm_benefits[index_test,]
index_val <- which(! index_no_train %in% index_test)
data_benefits.val <- dfdtm_benefits[index_val,]
```

```{r}
colnames(data_benefits.train)[which('a' %in% colnames(data_benefits.train))]
y <- data_benefits.train$fraudulent
seedReq1 <- .Random.seed
X1 <- model.matrix(fraudulent~., data = data_benefits.train)[,-1]
seedReq2 <- .Random.seed
#benefits_result.lasso <- cv.glmnet(X1, y, alpha = 0.99, family = "binomial")
benefits_result.lasso <- readRDS("RDS_Saves/BenefitsLASSOv2.RDS")
#plot(benefits_result.lasso)
#saveRDS(benefits_result.lasso, file = "RDS_Saves/BenefitsLASSOv3.RDS")
#summary(benefits_result.lasso)

benefits_coef.1se <- coef(benefits_result.lasso, s = "lambda.min")
benefits_coef.1se <- benefits_coef.1se[which(benefits_coef.1se != 0),]
lasso.words.benefits <- rownames(as.matrix(benefits_coef.1se))[-1]
#lasso.words <- coef.1se@Dimnames[[1]] [coef.1se@i][-1]
#summary(lasso.words.benefits)
benefits_coef.1se <- benefits_coef.1se[-1]
benefits_coef.1se
length(benefits_coef.1se)
```

```{r word cloud benefits for scams}
benefits_scam.glm <- benefits_coef.1se[which(benefits_coef.1se > 0)]
#benefits_scam.glm <- benefits_scam.glm[-1]  # take intercept out
names(benefits_scam.glm)[1:2]  # which words are positively associated with good ratings
#good.glm
#benefits_scam.fre <- sort(benefits_scam.glm, decreasing = TRUE) # sort the coef's
#benefits_scam.fre
round(benefits_scam.fre, 4)[1:2]
length(benefits_scam.fre)
# hist(as.matrix(good.fre), breaks=30, col="red") 
benefits_scam.word <- names(benefits_scam.fre)  # good words with a decreasing order in the coeff's


cor.special <- brewer.pal(8,"Dark2")  # set up a pretty color scheme
wordcloud(names(benefits_scam.glm), benefits_scam.glm,  # make a word cloud
          colors=cor.special, ordered.colors=F)
```

```{r word cloud benefits for reals}
benefits_reals.glm <- benefits_coef.1se[which(benefits_coef.1se < 0)]
#benefits_reals.glm <- benefits_reals.glm[-1]  # take intercept out
# names(benefits_reals.glm)[1:2]  # which words are positively associated with good ratings
#good.glm
# benefits_reals.fre <- sort(benefits_reals.glm, decreasing = TRUE) # sort the coef's
# benefits_reals.fre
# round(benefits_reals.fre, 4)[1:2]
# length(benefits_reals.fre)
# hist(as.matrix(good.fre), breaks=30, col="red") 
benefits_reals.word <- names(benefits_reals.fre)  # good words with a decreasing order in the coeff's


cor.special <- brewer.pal(8,"Dark2")  # set up a pretty color scheme
wordcloud(names(benefits_reals.glm), benefits_reals.glm * -1,  # make a word cloud
          colors=cor.special, ordered.colors=F)
```

```{r logistic model benefits}
wordfit <- glm(fraudulent ~ bonus + dental + employe + free + insur + offer + offic + time + vacat + year, dfdtm_benefits, family = "binomial") #0.436
#wordfit <- glm(fraudulent ~ great + competit + insur + free + earn + complet, dfdtm_benefits, family = "binomial")
#wordfit <- glm(fraudulent ~ abl + desir + level + person + role + skill + team + valid + will + word, dfdtm_benefits, family = "binomial")
# 0.464
summary(wordfit)

fit.fitted.test <- predict(wordfit, data_benefits.test, type="response")
fit.test.pred <- ifelse(fit.fitted.test > 1/2, "1", "0")
error.testing.fit.final <- mean(fit.test.pred != data_benefits.test$fraudulent)
error.testing.fit.final
```

```{r}
#abl        engin       inform        level       person   profession         sale       scienc         will
wordfit <- glm(fraudulent ~ abl + engin + inform + level + person + profession + sale + scienc + will, dfdtm_requirements, family = "binomial")
summary(wordfit)
fit.fitted.test <- predict(wordfit, data_requirements.test, type="response")
fit.test.pred <- ifelse(fit.fitted.test > 1/2, "1", "0")
error.testing.fit.final <- mean(fit.test.pred != data_requirements.test$fraudulent)
error.testing.fit.final
```

```{r}
# account       assist         best          can       comput         data       execut        field       financ 
#  0.206235254  0.078281196  0.009441806  0.160341135 -0.102909440 -0.003536444 -0.061876193  0.049460385 -0.047578369  0.158636867 
#      general        group         hire         home     industri        locat        mobil         must      network        place 
#  0.021251793  0.056733971 -0.009749587 -0.030149278  0.053509617 -0.039454112 -0.016741370  0.044819900 -0.350850672 -0.025475407 
#       prefer      project       promot       record       requir       salari       senior          set         site        small 
# -0.314862818 -0.042763559  0.102033348  0.001565125 -0.083164888 -0.208952082 -0.215816341  0.220988151 -0.180034215  0.045932001 
#      softwar    temporari         test         type        visit        youll

#wordfit <- glm(fraudulent ~ account + assist + best + can + comput + data + execut + field + financ + general + group + hire + home + industri + locat + mobil + must + network + place + prefer + project + promot + record + requir + salari + senior + set + site + small + softwar + temporari + test + type + visit, dfdtm_description, family = "binomial")

# achiev       appli      execut        fast        good    interest        join      prefer         set   temporari 
# -0.12080281  0.05484175 -0.09285484  0.10447607 -0.06145582 -0.21126359 -0.01999453 -0.09292082 -0.03574468  0.11974122  0.32631801 
#        year
# achiev        appli       assist       execut         fast         good     interest         join       prefer 
# -0.109167312  0.114273469 -0.120645805  0.008522469  0.125275623 -0.099728956 -0.241977515 -0.061402822 -0.112101450 -0.059423656 
#          set        small    temporari         tool         year 



#wordfit <- glm(fraudulent ~ account + assist + best + can + comput + data + execut + field + hire + industri + locat + mobil + must + network + prefer + project + record + salari + senior + set + softwar + temporari + test + visit, dfdtm_description, family = "binomial")

#wordfit <- glm(fraudulent ~ achiev + appli + assist + execut + fast + good + interest + join + prefer + set + temporari + tool +year, dfdtm_description, family = "binomial")
wordfit <- glm(fraudulent ~ achiev + appli + assist + execut + fast + good + join + prefer + set + temporari + tool, dfdtm_description, family = "binomial")
summary(wordfit)
fit.fitted.test <- predict(wordfit, data_description.test, type="response")
fit.test.pred <- ifelse(fit.fitted.test > 1/2, "1", "0")
error.testing.fit.final <- mean(fit.test.pred != data_description.test$fraudulent)
error.testing.fit.final
```


